---
output: github_document
---
![CI](https://github.com/DataStrategist/amitFuncs/workflows/CI/badge.svg?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# amitFuncs

Random convenience functions from a lazy person

## Installation

You can install the released version of amitFuncs from github by using:

``` {r}
# remotes::install_github("DataStrategist/amitFuncs")
```

## Exported Functions

### left, mid, right

Excel like convenience functions:

``` {r}
library(amitFuncs)
left("boom", 1)
right("boom", 1)
amitFuncs::mid("boom", 2, 2)

```

### gitLister

List all git repos within a certain folder. For example, to list all the repos in the folder above your current `getwd()`, type:

```{r}
tail(gitLister(paff = ".."), 5)
```
 

### libraryFinder

Finds all the libraries used in files modified within `x` days ago. For example, to list the libraries required for the current `getwd()` that have been modified in the past 2 weeks, type:

```{r}
libraryFinder(parentFolder = ".", howLong = 14, whatLib = "c:/temp/")
```

This will output a command that you can copypaste to install all those libraries into a `c:/temp`.
